\Title

### 2021-04-29 latex/paper/main.tex
First draft of simulation section, except for regulation.

Note that these parameters do not correspond to our simplified acrobot in Figure
\ref{fig:simple-acrobot-model}, but rather to the more general acrobot model in
Figure \ref{fig:acrobot-model}.
In particular, the inertia matrix and potential function are \textbf{not}
described by ~\eqref{eqn:acrobot-inertia}-\eqref{eqn:acrobot-potential}.
The correct \(M(q)\) and \(V(q)\) can be found in Wang's thesis
\cite{xingbo_thesis}.
If our VNHC injects energy into this acrobot, then we can infer that
VNHCs are robust to model mismatch.

@@

According to Theorem \ref{thm:acrobot-energy-stabilization}, the control
parameter \(I\) must be small.
While we could choose \(I\) arbitrarily small in simulations, we will eventually
compare these simulations with the physical experiments where \(I\) must be
large enough to overcome friction in leg motor.
Setting \(\bar{q}_a = 1\), we experimentally determined that \(I = 10\) is a
viable control value.
This is the value of \(I\) we used in all simulations and experiments.

\textbf{TODO: the injection and dissipation I is different, so we might not use
I = 10 for dissipation.}

@@

To validate the energy injection property of our VNHC, we simulated the acrobot
with initial condition \((q_u,p_u) = \left(\pi/32,0 \right)\) and plotted the
resulting orbit in Figure \ref{fig:acrobot-orbit}.

The set \(E_\pi := E(\pi,0)\) is outlined in black. 
Due to the model mismatch, \(E_\pi\) is no longer the boundary between
rotations and oscillations.
The oscillation domain is actually much larger: orbits rotate once they hit the
\(p_u\)-axis at \(\abs{p_u} \approx 0.15\), while \(E_\pi\) intersects the
\(p_u\)-axis at \(\abs{p_u} \approx 0.055\).
Despite this, the VNHC still injects energy into the acrobot.
The points where the orbit exits \(E_\pi\) are marked with black stars,
with the final departure marked by a red star.
After this final departure, the acrobot begins rotating and continues to gain
energy over time.

\begin{figure}[]
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_orbit.png}
    \caption{A simulation of the acrobot gaining energy.}
    \label{fig:acrobot-orbit}
\end{figure}

@@

@@

@@

\textbf{TODO: rework this section. In simulation we showed that we gain energy
continuously. Here we only gain energy up to speed 0.195 because of friction.}
Wang's acrobot has an encoder which measures \(q_u\) and
\(\dot{q}_u\).
Additionally, the leg actuator is a servo motor with a built-in PID controller
which provides measurements of \(q_a\).
To implement our VNHC, we estimated \(\dot{q}_a\) through sequential values of
\(q_a\) and computed \(p_u\) through \(p_u = e_1^T M(q) \dot{q}\).
We directly assigned the actuator setpoint at iteration \(k \in \mathbb{Z}_{> 0}\)
via \(q_a^{k} = \arctan(10 p_u^{k-1})\).
We then performed the following tests.

@@

\subsection{Summary of Results} 
These simulations and experiments demonstrate that VNHCs are excellent
tools for injecting energy.
In particular, energy injection through VNHCs appears to be robust against a
variety of disturbances, including significant model mismatch and sensor noise.

>>>>

Note that these parameters do not correspond to our simplified acrobot in Figure
\ref{fig:simple-acrobot-model}, but rather to the more general acrobot model in
Figure \ref{fig:acrobot-model}.
In particular, the inertia matrix and potential function are \textbf{not}
described by ~\eqref{eqn:acrobot-inertia}-\eqref{eqn:acrobot-potential}.
The correct \(M(q)\) and \(V(q)\) can be found in Wang's thesis
\cite{xingbo_thesis}.
\textbf{TODO: put them here if there is space}.
If our VNHC injects energy into this acrobot, then we can infer that
VNHCs are robust to model mismatch.

@@

@@

According to Theorem \ref{thm:acrobot-energy-stabilization}, the control
parameter \(I\) must be small if one wants the VNHC to inject energy.
While we could make \(I\) arbitrarily small in simulations, we will eventually
implement this VNHC on a physical system where \(I\) must be large enough to
overcome friction in leg motor.
Setting \(\bar{q}_a = 1\), we experimentally determined that \(I = 10\) is a
viable control value for energy injection.

We simulated the acrobot with initial condition 
\((q_u,p_u) = \left(\pi/32,0 \right)\) for \(30\) seconds and plotted the
resulting orbit in Figure \ref{fig:acrobot-in-orbit}.

The level set \(E_\pi\) with energy \(E(\pi,0)\) is outlined in black. 
Due to the model mismatch, \(E_\pi\) is no longer the boundary between
rotations and oscillations.
The oscillation domain is actually much larger: orbits rotate once they hit the
\(p_u\)-axis at \(\abs{p_u} \approx 0.15\), while \(E_\pi\) intersects the
\(p_u\)-axis at \(\abs{p_u} \approx 0.055\).
Despite this, the VNHC still injects energy into the acrobot.
The points where the orbit exits \(E_\pi\) are marked with black stars,
with the final departure marked by a red star.
After this final departure, the acrobot begins rotating and continues to gain
energy over time.

\begin{figure}[]
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_in_orbit.png}
    \caption{A simulation of the acrobot gaining energy.}
    \label{fig:acrobot-in-orbit}
\end{figure}

@@

According to Theorem \ref{thm:acrobot-energy-stabilization}, a negative value
of \(I\) should dissipate energy from the acrobot.
To test this, we initialized our acrobot with a rotation at the phase
\((q_u,p_u) = (0,0.18)\),  set \(I = -10\), and simulated the constrained
dynamics for \(30\) seconds.
The resulting orbit is plotted in Figure \ref{fig:acrobot-diss-orbit}. 
As is expected, the acrobot slows down over time.
We again highlight the locations where the orbit crossed the set \(E_\pi\) in
black, with the final crossing in red. 
After this crossing, the acrobot ceased rotating and its oscillations decayed to
zero.

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{acrobot_diss_orbit.png}
    \caption{A simulation of the acrobot dissipating energy.}
    \label{fig:acrobot-diss-orbit}
\end{figure}

@@

To test how VNHCs can perform energy regulation, we employed a simple supervisor
which toggles between injection and dissipation VNHCs to stabilize an
orbit which crosses the \(q_u\)-axis at some desired angle (for oscillations) or
the \(p_u\)-axis at some desired velocity (for rotations).
Specifically, one chooses some appropriate energy value \(E_0 > 0\) and a hysteresis
percentage \(\delta \in [0,1]\).
The supervisor enables the injection VNHC if 
\(E(q_u,p_u) < (1-\delta)E_0\), the dissipation VNHC if 
\(E(q_u,p_u) > (1+\delta) E_0\), and it keeps the leg angle constant if
\((1-\delta)E_0 \leq E(q_u,p_u) (1+\delta)\leq E_0\).

First, we wanted the acrobot to oscillate with a maximum body angle 
\(q_u = \pi/2\).
The corresponding energy is \(E_0 = E(\pi/2,0)\), and we set our hysteresis to
be \(\delta = 5\%\).
\textbf{TODO: do the energy regulation experiment and see the results.}

\subsection{Summary of Results}
The simulation results in this section demonstrate the energy regulation
capabilities of our VNHC.  
In particular, Theorem \ref{thm:acrobot-energy-stabilization} appears to work
even for acrobots whose limbs have differing masses and lengths.
The energy regulation supervisor does not

@@

\textbf{TODO: rework this section. In simulation we showed that we gain energy
everywhere. Here we only gain energy up to speed 0.195 because of friction.}
Wang's acrobot has an encoder which measures \(q_u\) and
\(\dot{q}_u\).
Additionally, the leg actuator is a servo motor with a built-in PID controller
which provides measurements of \(q_a\).
To implement our VNHC, we estimated \(\dot{q}_a\) through sequential values of
\(q_a\) and computed \(p_u\) through \(p_u = e_1^T M(q) \dot{q}\).
We directly assigned the actuator setpoint at iteration \(k \in \mathbb{Z}_{> 0}\)
via \(q_a^{k} = \arctan(10 p_u^{k-1})\).
We then performed the following tests.

@@

\subsection{Summary of Results} 
These experiments demonstrate that VNHCs are excellent tools for injecting
energy.
In particular, energy injection through VNHCs appears to be robust against a
variety of disturbances, including significant model mismatch, friction, and
sensor noise.
